\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
added some dsicussion of problem issues. more to follow.

>>>>

It is important to note that in the case of such problem points it is
non-trivial to judge whether this is because there is no physical
solution for the given parameter space point or whether a solution
exists but the fixed point iteration is unable to find the solution.
While \fs makes it as easy as possible to fin spectra, when studying
new models a physical understanding of the model is still essential
and this can help the user determine why the such problems arise.

Nonetheless \fs provides help for such cases in several ways. One may
adjust initial guesses specified in the FlexibleSUSY modle file, such
as changing the choice of HighScaleFirstGuess or altering
HighScaleMinimum and HighScaleMaximum which can be used to push the
iteration back towards where the solution should be if it gets off
track.

The modular design of FlexibleSUSY allows solver for the boudary
